---
title: "Getting Started with binomial"
author: "Thomas Bates"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial

The package `"binomial"` is a minimal implementation for representing a binomial distribution and it's computations. 

## Creating a `binomial distribution`

We can create a binomial distribution to do calculations with and plot using:

```{r}
bin_dist <- bin_distribution(trials = 5, prob = 0.5)
plot(bin_dist)
```

We can also create a cumulative distribution that keeps track of the overall
probability as the number of successes increases:

```{r}
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
plot(bin_cum)
```


## Creating a binomial random variable

We can create a binomial random variable that we can then use to summarize a binomial random variable. 

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
bin1
```

The `summary()` function gives you a nice table of binonmial random variable calculations:
```{r}
binsum1 <- summary(bin1)
binsum1
```
